\cvsection{Experience}

\begin{cventries}

  \cventry
    {IT Lead Programmer} % Job title
    {NYU Dibner IT} % Organization
    {Brooklyn, NY} % Location
    {Apr. 2019 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Program sensors and motors using Python for numerous projects to be used in NYU Libraries to help with student interaction. }
        \item {Model PCB's and solder components such that the hardware designs can interact with the Raspberry Pi’s to carry out the program.}
      \end{cvitems}
    }

  \cventry
    {Content Manager} % Job title
    {Design Technologies} % Organization
    {New York, NY} % Location
    {Nov. 2018 - Jan. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Updated the contents and design of myriad websites from 3 sub-companies; ELabNYC, ABCT, DesignTechnologies.}
		\item {Utilized WordPress for content updates, data entry, design modifications and reported bugs and errors to the site developers}
      \end{cvitems}
    }

  \cventry
    {Quality Assurance Analyst} % Job title
    {Barbarian} % Organization
    {New York, NY} % Location
    {Jun. 2018 - Aug. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created websites and updated new content for clients such as Samsung and ABInBev, for myriad desktop and mobile devices.}
		\item {Tested application features to fix front-end and back-end errors and delegated tasks to fix bugs by communicating through Jira software.}
      \end{cvitems}
    }

 % \cventry
 %   {Research Apprentice} % Job title
  %  {Columbia University, Department of Biomedical Engineering} % Organization
   % {New York, NY} % Location
    %{Jun. 2017 - Aug. 2017} % Date(s)
%    {
 %     \begin{cvitems} % Description(s) of tasks/responsibilities
  %      \item {Conducted research on the development of size-isolated microbubbles to obtain the most efficient and precise diameter of microbubbles.}
  %      \item {Presented research on Focused-Ultrasound to renowned researchers and scientists at the American Museum of Natural History.}
  %    \end{cvitems}
   % }    
\end{cventries}