\cvsection{Projects}

\begin{cventries}
  \cventry
    {} % Empty position
    {The Parking Lot Project} % Project
    {} % Empty location
    {} % Empty date
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Created a system to track population density of four zones at NYU Dibner Library to help students know which areas have seats available.}
		\item {Programmed Raspberry Pi's to work with ultrasound sensors installed in every seat to detect which seats are currently in use.}
      \end{cvitems}
    }
    
  \cventry
    {} % Empty position
    {Eternity - HackRPI} % Project
    {} % Empty location
    {} % Empty date
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Utilized Google Cloud and Trip Advisor API to create an iOS app to compete against 60+ teams in Rensselaer Polytechnic Institute.}
		\item {Developed an iOS app that facilitates awareness of daily resource consumption by tracking users' Carbon Footprint number.}
      \end{cvitems}
    }

  \cventry
    {} % Empty position
    {Uplift - HackNYU} % Project
    {} % Empty location
    {} % Empty date
    {
      \begin{cvitems} % Description(s) bullet points
      	\item {Competed with 100+ teams using API’s from Google and IBM; built with cloud computing from Firebase and IBM Watson's Machine Learning.}
		\item {Built an iOS app which creates an online community for the terminally ill by sharing their stories and connecting them with others patients.}
      \end{cvitems}
    }
    
    \cventry
    {} % Empty position
    {HydroHub - I2E Tournament} % Project
    {} % Empty location
    {} % Empty date
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Selected to be in 1 of 4 teams to create a product and compete based on the exhibition of its invention, innovation and entrepreneurship.}
		\item {Created a smart water bottle system which tracks water intake and temperature while displaying the data on an app and a built-in LCD screen.}
      \end{cvitems}
    }
    
    
    \cventry
    {} % Empty position
    {Smart Mouthguard} % Project
    {} % Empty location
    {} % Empty date
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Won the Academic and Faculty Award out of 8 teams after presenting group project to researchers and scientists at Columbia Labs.}
		\item {Constructed a mouthguard that can wirelessly transmit body temperature to an app and alert users when the temperature rises too high.}
      \end{cvitems}
    }
    
    \cventry
    {} % Empty position
    {TEDx Brooklyn Tech} % Project
    {} % Empty location
    {} % Empty date
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Chosen as 1 of 3 speakers to present a idea on TEDx Brooklyn Tech. to 300+ people, alongside renowned CEOs and entrepreneurs.}
		\item {Presented a talk on the effects of monetary wealth on an individuals happiness and its correlation to being content with life.}
      \end{cvitems}
    }
\end{cventries}